Effect_size_families

### 2019-03-03 Effect_size_families_plot.Rmd
edits

---
title: "Effect_size_families"
author: "Jose Barragan"
date: "3 March 2019"
output: html_document
---

@@

p1<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)
p1 + geom_point(show.legend = FALSE,aes(color=factor(Family))) +
  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

```

>>>>

---
title: "Effect_size_families"
author: "Jose Barragan"
date: "3 March 2019"
output:
  pdf_document: default
  html_document: default
---

@@

p1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/soly_effect_size_family.RData")

p2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/sial_effect_size_family.RData")

p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/pein_effect_size_family.RData")

p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/ippu_effect_size_family.RData")

p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/ipaq_effect_size_family.RData")

p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/ersa_effect_size_family.RData")

p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/caan_effect_size_family.RData")

p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/brra_effect_size_family.RData")

p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/brol_effect_size_family.RData")

p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

 #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
grid.newpage()
 grid.draw(arrangeGrob(cbind(ggplotGrob(p1),ggplotGrob(p2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
```
